Modern Graph Generators: A Survey

### 2018-08-09 introduction.tex
pass on the Intro/title/RW

%One of the most popular data structures in the world of computer science are graphs.
Graphs are ubiquitous data structures that span a wide array of disciplines
and are subject of study in several subfields of computer science.
Nowadays, due to the dawn of numerous tools and applications manipulating
graphs, they are adopted as a rich data model in many data science use
cases involving disparate domain knowledge, mathematical foundations and
computer science. Interconnected data is oftentimes used to encode domain-specific
use cases, such as recommendation networks, social networks,
protein-to-protein interactions, geolocation networks, and fraud detection analysis networks, to
name a few.
% ANGELA: I do not think we should cite Neo4J, which is a graph database.
%They enable to represent complex information in a simple and yet powerful way supported by a strong mathematical background. With the dawn of the new millennium which brought numerous novel technologies and applications, the graphs have become even more popular. There has appeared a number of use cases\footnote{\url{https://neo4j.com/use-cases/}} (such as fraud detection, recommendation engines, social networks etc.) where graphs represent the linked information.

@@

In this survey, we provide a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks. Our aim is to cover a wide range of currently popular areas of graph data processing. In particular, we consider graph generation in the areas of graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities. Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

\begin{enumerate}
  \item Despite the differences of the covered areas, the requirements for the graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
  \item The selected classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.
\end{enumerate}

To conclude the comparative study and provide a comprehensive view of the field,  we also discuss open challenges and missing features of graph generators in view of identifying future challenges in data science.

\paragraph*{Contributions} Our survey reviews the representatives of graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, our work is the first surveying the broad
landscape of graph data generators spanning different data science applications and
targeting diverse computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IoT, Telecommunication and graph streaming generators,
and Machine Learning and graph mining generators. A comprehensive study of
graph generators is missing for many of the specific subfields mentioned
above.

A limited subset of graph database
generators, parallel and distributed graph processing generators, along
with a few of the Semantic Web data generators presented in our survey have
been discussed in a related book chapter
\cite{BFHI18} while cross-comparing them with respect to input, output,
supported workload, data model and query language, along with the
distinguished chokepoints. However, the provided classification is
inherently data-driven and not meant to serve the purpose of letting any
researcher or practitioner interested in data science make a guided
choice of the desired
generator based on its functional and goal-driven features (such as the application domain,
the supported operations and the key configuration options).
Moreover, our work is much broader and targets graph generators of several
diversified communities, not limiting its scope to few generators of the database
and graph processing communities.

Graph generators matching graph patterns used in data mining have been
studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
focusing on mostly occurring patterns, such as power laws, size of graph diameters
and community structure. The considered graph generators are compared in
terms of graph type, degree distributions, exponentiality, diameter and
community effects. We refer the reader to this survey for taxonomies
involving these properties, whereas we provide here a functionality-driven
taxonomy across all the categories of graph generators that we consider.
We also point out that this survey is outdated as it does not consider the
graph mining generators that fervently appeared in the last decade.

\TODO{Check with Arnau}

Aggarwal and Subbian \cite{AggarwalS14} have surveyed evolution analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks based on
Densification Power Law (DPL) and shrinking diameters \cite{LeskovecKF05} and community-guided
attachment properties \cite{LeskovecKF05} is then considered, along with tackling Kronecker
recursion with recursive tensor multiplication \cite{AkogluMF08}.

\TODO{Better highlight the differences when Sherif's part is in.}

>>>>

%One of the most popular data structures in the world of computer science are graphs.
Graphs are ubiquitous data structures that span a wide array of scientific disciplines
and are a subject of study in several subfields of computer science.
Nowadays, due to the dawn of numerous tools and applications manipulating
graphs, they are adopted as a rich data model in many data-intensive use
cases involving disparate domain knowledge, mathematical foundations and
computer science. Interconnected data is oftentimes used to encode domain-specific
use cases, such as recommendation networks, social networks,
protein-to-protein interactions, geolocation networks, and fraud detection analysis networks, to
name a few.
% ANGELA: I do not think we should cite Neo4J, which is a graph database.
%They enable to represent complex information in a simple and yet powerful way supported by a strong mathematical background. With the dawn of the new millennium which brought numerous novel technologies and applications, the graphs have become even more popular. There has appeared a number of use cases\footnote{\url{https://neo4j.com/use-cases/}} (such as fraud detection, recommendation engines, social networks etc.) where graphs represent the linked information.

@@

In this survey, we provide a comprehensive overview of the state-of-the-art
modern
graph generators by focusing on those that are pertinent and suitable for
data-intensive tasks. Our aim is to cover a wide range of currently popular
areas of graph data processing. In particular, we consider graph generation
in the areas of graph databases, graph data mining, graph streaming and
machine learning communities, alongside community detection, social
networks and IoT communities. Despite the disparate requirements of modern graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators. The reasons for this scope and classification are as follows:

\begin{enumerate}
  \item Despite the differences of the covered areas, the requirements for
modern graph data generators can be similar in particular cases. Reusing or learning from tools in other fields can thus bring new opportunities for both researchers and practitioners.
  \item The selected classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.
\end{enumerate}

To conclude the comparative study and provide a comprehensive view of the
field,  we also discuss open challenges and missing requirements of modern
graph generators in view of identifying their future extensions to new emerging fields.

\paragraph*{Contributions} Our survey revisits the representatives of
modern graph data generators and summarizes their major features. The comprehensive review and analysis make this paper useful for motivating new graph data generation techniques as well as serving as a technical reference for selecting suitable solutions. In particular, the introductory categorization and comparative study enables the reader to quickly get his/her bearings in the field and identify a subset of generators of his/her interest. Since we do not limit the survey to a particular area of graph data management,  the reader can get a broader scope in the field. Hence, while practitioners can find a solution in another previously unexpected area, researchers can identify new target areas or exploit successful results in new fields. Last but not least, we identify general open problems of graph data synthesis and indicate possible solutions to show that it still forms a challenging and promising research area.

@@

To the best of our knowledge, our work is the first surveying the broad
landscape of graph data generators spanning different data-intensive applications and
targeting many computer science subfields. In particular, we cover graph database
generators, graph processing generators, social networks and community detection
generators, Semantic Web data generators, graph
analytics generators, IoT, Telecommunication and graph streaming generators,
and Machine Learning and graph mining generators. A comprehensive study of
graph generators is yet missing for many of the specific subfields mentioned
above.

A limited subset of graph database
generators, parallel and distributed graph processing generators, along
with a few of the Semantic Web data generators presented in our survey have
been discussed in a related book chapter
\cite{BFHI18} while cross-comparing them with respect to input, output,
supported workload, data model and query language, along with the
distinguished chokepoints. However, the provided classification is
inherently database-oriented. 
In our work, we provide a more comprehensive and broader classification 
 serving the purpose of letting any
researcher or practitioner interested in data generation make a wise
choice of the desired graph 
generator based on its functional and goal-driven features (such as the application domain,
the supported operations and the key configuration options).
Moreover, in contrast with \cite{BFHI18}, our work encompasses graph generators of several
diverse communities, not limiting its scope to a few generators of the database
and graph processing communities.

Graph generators matching graph patterns used in data mining have been
studied in \cite{Chakrabarti:2006:GML:1132952.1132954},
focusing on mostly occurring patterns, such as power laws, size of graph diameters
and community structure. The considered graph generators are compared in
terms of graph type, degree distributions, exponentiality, diameter and
community effects. We refer the reader to this survey for taxonomies
involving these properties, whereas we provide here a functionality-driven
taxonomy across all the categories of graph generators that we consider.
We also point out that this survey is outdated as it does not consider the
graph mining generators that fervently appeared in the last decade.
We fill the gap of more recent social network and graph analytics generators
respectively in Section 3.4 and 3.5.

%\TODO{Check with Arnau}

Aggarwal and Subbian \cite{AggarwalS14} have surveyed evolution analysis in
graphs, by primarily focusing on data mining maintenance methods and on analytical
quantification and explanation of the changes of the underlying networks.
A brief discussion on evolutionary
network data generators is carried out in
the paper. The data generation of evolutionary networks based on
Densification Power Law (DPL) and shrinking diameters \cite{LeskovecKF05} and community-guided
attachment properties \cite{LeskovecKF05} is then considered, along with tackling Kronecker
recursion with recursive tensor multiplication \cite{AkogluMF08}.
We refer the reader to this survey for evolutionary network generators and
we further discuss the open challenges of evolving graph data in Section 5. 
%\TODO{Better highlight the differences when Sherif's part is in.}

### 2018-08-09 main.tex
Missing parts of intro added
Sherif Changes
pass on the Intro/title/RW

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Graph Generators for Data Science: A Survey}

% Title portion
%\title{Graph Data Generators in the World of Big Data}
\title{Graph Generators for Data Science: A Survey}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{King Saud bin Abdulaziz University for Health Sciences, Saudi Arabia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
The abundance of interconnected data has fueled the design and implementation of graph generators reproducing real-world linking properties, or gauging the effectiveness of graph algorithms, techniques and applications manipulating these data. We consider graph generation targeting multiple subfields, such as graph databases, graph data mining, graph streaming and machine learning communities, alongside community detection, social networks and IoT communities. Despite the disparate requirements of graph generators throughout these communities, we analyze them under a common umbrella, reaching out the functionalities, the practical usage, and the supported operations of graph generators.
We argue that this classification is serving the need of providing data scientists, researchers and practitioners with the right data generator at hand for their work.

This survey provides a comprehensive overview of the state-of-the-art graph generators by focusing on those that are pertinent and suitable for data science tasks. Finally, we discuss open challenges and missing features of graph generators in view of the evolution of data science.
\end{abstract}

@@

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018. Graph Generators for Data Science: A Survey.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

\input{introduction}
\input{preliminaries}
\input{comparison}
%\input{classification}
\input{generators}
%\input{comparison2}
\input{challenges}
\input{conclusion}

>>>>

% Page heads
\markboth{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr}{Modern Graph Generators: A Survey}

% Title portion
%\title{Graph Data Generators in the World of Big Data}
\title{Modern Graph Generators: A Survey}
\author{
ANGELA BONIFATI
\affil{Lyon 1 University, France}
IRENA HOLUBOV\'{A}
\affil{Charles University, Prague, Czech Republic}
ARNAU PRAT-P\'{E}REZ
\affil{DAMA-UPC, Universitat Polit\`ecnica de Catalunya, Spain}
SHERIF SAKR
\affil{University of Tartu, Estonia}
}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.

\begin{abstract}
The abundance of interconnected data has fueled the design and
implementation of graph generators reproducing real-world linking
properties, or gauging the effectiveness of graph algorithms, techniques
and applications manipulating these data. We consider graph generation
across multiple subfields, such as graph databases, graph data mining,
graph streaming and machine learning communities, alongside community
detection, social networks and IoT communities. Despite the disparate
requirements of modern graph generators throughout these communities, we
analyze them under a common umbrella, reaching out the functionalities, the
practical usage, and their supported operations.
We argue that this classification is serving the need of providing scientists, researchers and practitioners with the right data generator at hand for their work.

This survey provides a comprehensive overview of the state-of-the-art
modern graph generators by focusing on those that are pertinent and
suitable for several data-intensive tasks. Finally, we discuss open
challenges and missing requirements of current graph generators along with their future extensions to new emerging fields.
\end{abstract}

@@

\acmformat{A. Bonifati, I. Holubov\'{a}, A. Prat-P\'erez, S. Sakr, 2018.
Modern Graph Generators: A Survey.}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

@@

\input{introduction}
%\input{preliminaries}
\input{comparison}
%\input{classification}
\input{generators}
%\input{comparison2}
\input{data_sets}
\input{challenges}
\input{conclusion}
